\Large \bf One-Step, Three-Factor Authentication With Custom-Fit, In-Ear EEG

### 2017-02-15 paper.tex
proofs

Past work has exploited tacit skills (skills we know how to do, but cannot readily explain our method for doing, e.g. riding a bike or walking \cite{Bojinov2012}. In practice, these skills require time to learn, and their visible performance could open opportunities for recording and replay attacks.

@@

Even consumer-grade headsets can be uncomfortable to wear, and are awkwardly visible to observers. Earbuds present a more discreet, comfortable location for an EEG sensor, as many people already wear earbuds in day-to-day life.

>>>>

Past work has exploited tacit skills (skills we know how to do, but cannot readily explain our method for doing, e.g. riding a bike or walking \cite{Bojinov2012}. In practice, these skills require time to learn, and the fact that they are performed visibly could open up opportunities for recording and replay attacks.

@@

Even consumer-grade headsets can be uncomfortable to wear, and are awkwardly visible to outside observers. Earbuds present a more discreet, comfortable location for an EEG sensor, as many people already wear earbuds in day-to-day life.
